---
title: "Mini-Project 2"
author: "Amelia Stapleton and Cassie Naranjo"
date: "3/22/2019"
output: html_document
code_folding: show
---

**Background (500 words):**
The data graphics below depict data from the Federal Election Commission and represent the 2011–2012 federal election cycle. 

All data in this project was provided by the Federal Election Commission (FEC), who, among other things, makes campaign finance information assessible to the public. On their website one can find files which contain finance data on all committees, campaigns, and candidates for each election cycle. 

Using the Federal Election Comission data, we wanted to look at variations incumbency re-election of candidates. In order to do this using these two data tables, House Elections and Candidates, we filtered, selected, and mutated the data to produce data graphics that would tell us how likley a candidate would be to be re-elected.

**What can we learn from these data graphics?**

These graphics can tell us how likely a candidate who was already in office in New York, California, or Texas was to be re-elected in their respective state in the 2011 - 2012 election cycle and whether or not that differs between democrats and republicians.


```{r, message = FALSE, echo = FALSE}
## Loading the data

## Here we are loading the libraries and data from the FEC data set that we need to create our data graphic. We will use the tidyverse ggplot features, dplyr features to wrangle the data, ggthemes to make our graphic more aestheically pleasing, and RColorBrewer to load in specific colors into our graphic.

library(tidyverse)
library(dplyr)
library(ggthemes)
library(RColorBrewer)
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r, message = FALSE, echo = FALSE}
##This chunk of code serves to filter out the columns we want from candidates data set. We only want to look at the year 2012 so we are filtering out all the other years and we also need to select for the cand_id in order to create a common variable between this and another data set.

new_c <- candidates %>%
  filter(cand_election_yr == "2012") %>%
  select(cand_id,cand_election_yr)
```

```{r, message = FALSE, echo = FALSE}
## This chunk is filtering out what we want from house_elections data frame. We are only interested in the incumbent = TRUE data, along with the candidate_name, states, party, and whetehr or not the candidate was re-elected. We also needed to mutate cand_id to equal fec_id to create a common variable in order to join the datasets.

new_h_e <- house_elections %>%
  filter(incumbent == "TRUE") %>%
  mutate(cand_id = fec_id) %>%
  select(cand_id, candidate_name, state, incumbent, party, ge_winner)
```

```{r, message = FALSE, echo = FALSE}
##Here we are joining the two data frames we are interested in using the common variable of cand_id.

MP2_table <- new_h_e %>%
  inner_join(new_c, by = c("cand_id" = "cand_id"))
```

```{r message = FALSE, echo = FALSE}
##This chunk serves to create a function to generate tables for different states that will summarize the amount of candidates who were re-elected and who make up each party.

table_function <- function(state_arg) {
  MP2_table %>%
     filter(state == state_arg) %>%
  group_by(party, ge_winner) %>%
  summarize(N = n())
}
```

```{r, message = FALSE, echo = FALSE}
##Here we are plugging in different state arguments into our function to generate plots for each state.

plot_CA <- table_function(state_arg = "CA")
plot_NY <- table_function(state_arg = "NY")
plot_TX <- table_function(state_arg = "TX")
```

```{r, message = FALSE, echo = FALSE}
##This chunk is creating a function for each of our data graphics. We wanted to make a stacker bar graphic and have different colors represent democratic winners and losers as well as republican winners and losers.

plot_function <- function(data_arg) {
  ggplot(data = data_arg, aes(x = party, y = N, fill = interaction(party, ge_winner))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(y = "Number of Incumbent Candidates", x = "Political Party") +
    scale_fill_manual(values = c("#9ecae1", "#fc9272", "#3182bd", "#de2d26"), name = "Condition", labels = c("Democratic Nonwinner", "Republican Nonwinner", "Democratic Winner", "Republican Winner"))+
  scale_x_discrete(breaks = c("D", "R"), labels = c("Democratic", "Republican")) +
  ggthemes::theme_tufte() +
  theme(plot.title = element_text(size=15.5, face='bold'),
axis.title.x = element_text(size =14), axis.title.y = element_text(size = 14), axis.ticks.length = (unit(.20, "cm")))
}

```

**Data Graphics:**
We created a plot function to generate the following graphics for California, New York, and Texas. On the bar plots, the x-axis is displaying the political parties, Democratic and Republican, and the y-axis is displaying the number of incumbent candidates. The key on the righthandside displays the combinations of conditions this data graphic is displaying along with the colors that represent them. We also used an annotation feature to display on the data graphic the percentages of the winners for each party in each state to highligh what each graphic tells us.

```{r}
plot_function(data_arg = plot_CA) +
  labs(title = "How Likely is a Candidate from California To Be Re-Elected? (2012)") +
  annotate("text", x = 1, y = 15, label = "87%", color = "white", size = 8, fontface = 'bold') +
  annotate("text", x = 2, y =7, label = "80%", color = "white", size = 8, fontface = 'bold')
```


*Results: This plot tells us that there are more incumbent democratic candidates in California and that these incumbent candidates were also more likely to be re-elected in the general election compared to republican incumbent candidates. Incumbent Democratic candidates were 87% likely to be re-elected whereas Republican incumbent candidates were 80% likely.*

```{r}
plot_function(data_arg = plot_NY) +
  labs(title = "How Likely is a Candidate from New York To Be Re-Elected? (2012)") +
  annotate("text", x = 1, y = 9, label = "94%", color = "white", size = 8, fontface = 'bold') +
  annotate("text", x = 2, y = 2.5, label = "71%", color = "white", size = 8, fontface = 'bold')
```


*Results: This plot tells us that are also more incumbent Democratic candidates than incumbent Republican candidates in New York and that these incumbent candidates were also more likely to be re-elected in the general election compared to Republican incumbent candidates. Incumbent Democratic candidates were 94% likely to be re-elected whereas Republican imcumbent candidates were 71% likely.*

```{r}
plot_function(data_arg = plot_TX) +
  labs(title = "How Likely is a Candidate from Texas To Be Re-Elected? (2012)") +
  annotate("text", x = 1, y = 4, label = "88%", color = "white", size = 8, fontface = 'bold') +
  annotate("text", x = 2, y = 12, label = "95%", color = "white", size = 8, fontface = 'bold')
```


*Results: This plot tells us that are more incumbent Republican candidates in Texas than incumbent Democratic candidates and that they were more likely to be re-elected in the general election compared to Democratic incumbent candidates. Incumbent Republican candidates were 95% likely to be re-elected whereas Democratic imcumbent candidates were only 88% likely.*

**Overall Conclusions**

When looking at all of these plots in unison, it is very clear that regardless of party, incumbent candidates were more likely to be re-elected in 2012 than the non-incumbant candidates. Therefore, one can conclude that once a candidate holds office, he or she is has a better chance of keeping their seat in future elections.

*Word Count*
```{r, message = FALSE, echo = FALSE}
##Word Count
wordcountaddin::word_count()
```

